Characterisation of transient resonances in extreme-mass-ratio-inspirals

### 2014-08-04 res_char.tex
paper summary

@@

\section{Problem formulation}

\subsection{Kerr geodesics}

@@

\section{Properties of Transient Resonances}
\subsection{Location}

@@

\section{Astrophysical implications}

@@

\subsection{Population results}

@@

\section{Concluding remarks}

>>>>

In \secref{problem}, we formulate the specific problem at hand: that of geodesic motion in Kerr spacetime, perturbed by the gravitational self-force. We then study generic properties of transient resonances in \secref{properties}, detailing their location in parameter space, the time-scales over which they affect the motion and the resulting GW flux enhancements. Specific examples are considered to illustrate the effects of resonances at the start of \secref{astrophysics}, before finally turning to an astrophysical population in \secref{population}. Our conclusions can be found in \secref{conclusion}.

@@

\section{Problem formulation}
\label{sec:problem}
\subsection{Kerr geodesics}

@@

\section{Properties of Transient Resonances}
\label{sec:properties}
\subsection{Location}

@@

\section{Astrophysical implications}
\label{sec:astrophysics}

@@

\subsection{Population results}
\label{sec:population}

@@

\section{Concluding remarks}
\label{sec:conclusion}
